\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[greek,english]{babel}
\usepackage{alphabeta} 
\usepackage[pdftex]{graphicx}
\usepackage[top=1in, bottom=1in, left=0.75in, right=0.75in]{geometry}
\linespread{1}
\setlength{\parskip}{8pt plus2pt minus2pt}
\widowpenalty 10000
\clubpenalty 10000
\newcommand{\eat}[1]{}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\usepackage[official]{eurosym}
\usepackage{enumitem}
\setlist{nolistsep,noitemsep}
\usepackage[hidelinks]{hyperref}
\usepackage{cite}
\usepackage{lipsum}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                              %
% Zachary DeLuca                                               %
% ECE 351 Section 53                                           %
% Lab 00                                                       %
% Due: Jan 24                                                  %
%                                                              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{ECE 351 Lab 0}
\author{Zachary DeLuca  }
\date{January 17th 2023}

\begin{document}

\maketitle
\HRule \\[1mm]
\section{Introduction}
In this lab we will be introduced to LaTeX and python. In this document, I will attempt to make a decent looking report using the OverLeaf LaTeX editor, and later I will attempt to upload my python code to GitHub. Within the body of this document I shall throw in some filler text to demonstrate what a real report might look like.
\section{Summer Gone By}
        By no means do I expect any grader to read the entirety of the following. 
    This past summer was the first in which I was employed in an internship. I worked for a subsidiary of Boise State University known as TechHelp. My position title was Student Design Engineer, and my main function was to be able to help clients with the prototyping process. I was to assist people unfamiliar with design and manufacturing develop a design and prototype, along with informing them of the manufacturing considerations. 

    Unfortunately, I only had one client I was able to work with and he came in the last week I worked there, so the majority of the time I spent there was more focused on learning how to use certain tools and machines, and also learning about design software and techniques. 

    Besides the topic of my employment, I was able to take a road trip from Coeur d'Alene to Pocatello in order to meet up with friends and watch performances of the traveling troupe known as Montana Shakespeare in the Park on the ISU campus and then again in Salmon, ID. 
    
\section{Summer Yet to Pass}
This upcoming summer, I have very few plans as I have an underdeveloped ability to plan for the future. My only goals are to obtain a position in an internship, hopefully one close to Coeur d'Alene. I also plan to spend more time with family over the summer as I moved to Moscow for school and see them sometimes on weekends. 
\section{Desires of The Laboratory}
In probably the most important part of this report, I hope to leave this lab with a collection of new experience in working with either new tools or techniques. Given what I have seen so far, I suspect I will be able to leave somewhat proficient in python and familiar with GitHub and the git repository system.  

\section{Conclusion}

Every report needs a conclusion so here is the conclusion for this lab. I was able to utilize certain tools within LaTex to write this report. And thus this labs is concluded.
\end{document}
